\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm} LFEUI - Investigation Proposal \\ \vspace{4mm} {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-1mm}

### 2023-12-02 text/proposta/prop.tex
beam energy

\begin{enumerate}
  \item Accelerator Startup;
  \item Calibration of the detectors with a sample of known composition;
  \item Obtaining the energy spectrums of both samples;
  \item Analysis of the results.
\end{enumerate}

@@

In order to choose the energy of the beam we need to take into account the cross section of the reaction between the the protons and the Li-7. We

\begin{center}
  \includegraphics[width=0.95\linewidth]{../images/Li_crosssection_energy.jpeg}
  \captionof{figure}{Cross section of the reaction between protons and Li-7 as a function of the beam energy.}
\end{center}

>>>>

\begin{enumerate}
  \item Accelerator Startup;
  \item Calibration of the detectors with a sample of known composition;
  \item Obtaining the energy spectrums of both samples with the appropriate beam energy;
  \item Analysis of the results.
\end{enumerate}

@@

In order to choose the energy of the beam we need to take into account the cross section of the reaction between the the protons and the Li-7.
We collected data from the IBANDL \cite{IAEA_EXFOR} database for this reaction in a range of $[0.5,7]$ MeV and plotted it in the following graph:

\begin{center}
  \includegraphics[width=0.95\linewidth]{../images/Li_crosssection_energy.jpeg}
  \captionof{figure}{Cross section of the reaction between protons and Li-7 as a function of the beam energy.}
  \label{fig:crosssection}
\end{center}

We are only interested in the energy range of $[0.5,5]$ MeV because the energy of the beam is limited by the accelerator.
As we can see in figure \ref{fig:crosssection}, the cross section of the reaction is maximum in the $[2.5,3]$ MeV range. 
Therefore, since we want to detect the Li-7 in the samples, we should choose the energy of the beam to be in this range.
